%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%--------------------------------------------------------- 
  \cventry
    {Institute for Aerospace Studies{\enskip\cdotp\enskip}Space and Terrestrial Autonomous Robotic Systems (STARS) Lab} % Job title
    {Graduate Researcher{\enskip\cdotp\enskip}University of Toronto} % Organization
    {Toronto, Canada} % Location
    {2018 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Thesis focused on improving the robustness of visual perception algorithms for autonomous vehicles.}
        \item {Developed a real-time, self-supervised deep learning-based camera parameter regression system.}
        \item {Conducted real-world visual odometry driving experiments using vehicles equipped with monocular cameras.}
        \item {System resulted in an increased number of sequential inlier feature matches in challenging lighting conditions.}
        \item {Increased inlier feature count resulted in robust inter-frame pose estimates in monocular visual odometry applications.}
         \item {Made extensive use of modern state estimation, sensor calibration, and visual perception algorithms.}
        \item {Collected a novel training dataset for the self-supervised training of a custom convolutional neural network.}
      \end{cvitems}
    }
    
  \cventry
    {ROB301: Introduction to Robotics{\enskip\cdotp\enskip}Division of Engineering Science} % Job title
    {Laboratory Teaching Assistant{\enskip\cdotp\enskip}University of Toronto} % Organization
    {Toronto, Canada} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in the development of state estimation, perception and control laboratory experiments in ROS.}
        \item {Gained expertise with sensor calibration, sensor fusion algorithms, and using various probabilistic filtering techniques.}
      \end{cvitems}
    }
    
%  \cventry
%	{Engineering and Operations} % Job title
%	{Engineer-in-Training{\enskip\cdotp\enskip}London Hydro Inc.} % Organization
%	{London, Canada} % Location
%	{2017-2018} % Date(s)
%	{
%	  \begin{cvitems} % Description(s) of tasks/responsibilities
%	  	\item {Facilitated the development of small-scale solar generation projects with external clients.}
%        \item {Assisted in the development of technical standards for engineering equipment.}
%	  \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
